---
title: "Factors Influencing Golf Earnings"
subtitle: "Linear Regression"  
author: "Tyler Battaglini & Ryan Lebo"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)

# Detect, install and load packages if needed.
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
if (!require("MASS")) {
   install.packages("MASS")
   library(MASS)
}
if (!require("nleqslv")) {
   install.packages("nleqslv")
   library(nleqslv)
}
#
if (!require("pander")) {
   install.packages("pander")
   library(pander)
}

if (!require("psych")) {   
  install.packages("psych")
   library(psych)
}
if (!require("MASS")) {   
  install.packages("MASS")
   library(MASS)
}
if (!require("ggplot2")) {   
  install.packages("ggplot2")
   library(ggplot2)
}
if (!require("GGally")) {   
  install.packages("GGally")
   library(GGally)
}
if (!require("car")) {   
  install.packages("car")
   library(car)
}
if (!require("dplyr")) {   
  install.packages("dplyr")
   library(dplyr)
}
if (!require("caret")) {   
  install.packages("caret")
   library(caret)
}
if (!require("readxl")) {   
  install.packages("readxl")
   library(readxl)
}
if (!require("openxlsx")) {   
  install.packages("openxlsx")
   library(openxlsx)
}
if (!require("forecast")) {   
  install.packages("forecast")
   library(forecast)
}
# specifications of outputs of code in code chunks
knitr::opts_chunk$set(echo = TRUE,      # include code chunk in the output file
                      warnings = FALSE,  # sometimes, you code may produce warning messages,
                                         # you can choose to include the warning messages in
                                         # the output file. 
                      messages = FALSE,  #
                      results = TRUE,
                      
                      comment = NA       # you can also decide whether to include the output
                                         # in the output file.
                      )   
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```


<!-- every new slide is created under three dashes (---) -->

<!-- (<h1) makes the title for the slide -->

<h1 align="center"> Table of Contents</h1>
<BR>


.pull-left[
- Introduction
- Variables
- Research Question
- Exploratory Data Analysis
- Linear Model
- Log Model
- Bootstrapping
- Model Selection
- Conclusion



]





---

<h1 align = "center"> Introduction <font color="orange"></font></h1>
<BR>
.pull-left[
- PGA 2004 data set (196 participants)
- What is the PGA?
- Data set provides (earnings and player stats)

]





---
<h1 align = "center"> Variables <font color="orange"></font></h1>
<BR>

.pull-left[
- Name
- Age
- Avg Drive
- Driving Accuracy
- Greens in Regulation
- Avg Number of Putts

]

.pull-right[
- Save Percentage
- Money Rank
- Number of Events
- Total Winnings
- Average Winnings

]

---
<h1 align = "center"> Research Question <font color="orange"></font></h1>
<BR>

- What variables affect the players winnings of this given season?
- Looking at average drive vs earnings


---
## Exploratory Data Analysis

- Check for high correlation
- Take out missing observations
- Remove some variables


```{r include=FALSE}
url <- "https://users.stat.ufl.edu/~winner/data/pga2004.dat"
pga_data <- read.table(url, header = FALSE, fill = TRUE)
pga_data$V1 <- NULL
colnames(pga_data) <- c("Player_name", "Player_Age", "Average_Drive", "Driving_Accuracy", "Greens_on_reg", 
                        "Average_number_putts", "Save_Percent", "Money_Rank",
                        "Number_events", "Total_Winnings", "Average_Winnings")
colSums(is.na(pga_data))
pga_data_clean <- na.omit(pga_data)
ggplot(pga_data_clean, aes(x = Average_Drive, y = Average_Winnings)) +
  geom_point() +
  geom_smooth(method = "lm", col = "green") +
  labs(title = "Scatter Plot of Average Drive vs. Average Winnings", x = "Average Drive", y = "Average Winnings")
str(pga_data_clean)
remove_low_drives <- function(pga_data_clean) {
  filtered_data <- pga_data_clean %>%
    filter(Average_Drive >= 150)
  
  return(filtered_data)
}
pga_data_filtered <- remove_low_drives(pga_data_clean)
```

```{r echo=FALSE, fig.width=7, fig.height=4, out.width='80%'}
ggplot(pga_data_filtered, aes(x = Average_Drive, y = Average_Winnings)) +
  geom_point() +
  geom_smooth(method = "lm", col = "green") +
  labs(
    title = "Scatter Plot of Average Drive vs. Average Winnings (Filtered)",
    x = "Average Drive",
    y = "Average Winnings"
  ) +
  theme_minimal() 
```

---
<h1 align = "center"> Linear Model <font color="orange"></font></h1>
<BR>


- Non-normal distribution
- Several Outliers
- Non-constant variance


```{r include=FALSE, fig.width=4, fig.height=2}
pga_data_filtered$Age_Above_30 <- pga_data_filtered$Player_Age > 30

head(pga_data_filtered$Age_Above_30)
pga_data_filtered <- pga_data_filtered %>% select(-Player_name, -Driving_Accuracy, -Total_Winnings, -Average_number_putts, -Money_Rank, -Player_Age)
kable(head(pga_data_filtered))

# Standardizing Average_Winnings using z-scores
pga_data_filtered$Standardized_Winnings <- scale(pga_data_filtered$Average_Winnings)

# Updating the multiple regression model with standardized winnings
full.model<- lm(Standardized_Winnings ~ Average_Drive + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, 
                          data = pga_data_filtered)

# Summary of the updated model
summary(full.model)

```


```{r echo=FALSE, fig.width=4, fig.height=2}
par(mfrow=c(1,3))
plot(full.model)

```

---

<h1 align = "center"> Linear Model Cont. <font color="orange"></font></h1>
<BR>

.pull-left[

- All below 5
- Little to no multicollinearity

]

---
## 

<div style="display: flex; justify-content: center; align-items: center; height: 80vh; font-size: 50px;">
  Box-Cox Transformation
</div>

---
## Box-Cox Transformation

- All the lambda values are close to 0
- Proceed with log transformation


```{r include=FALSE}
url <- "https://users.stat.ufl.edu/~winner/data/pga2004.dat"
pga_data <- read.table(url, header = FALSE, fill = TRUE)
pga_data$V1 <- NULL
colnames(pga_data) <- c("Player_name", "Player_Age", "Average_Drive", "Driving_Accuracy", "Greens_on_reg", 
                        "Average_number_putts", "Save_Percent", "Money_Rank",
                        "Number_events", "Total_Winnings", "Average_Winnings")
head(pga_data)

colSums(is.na(pga_data))
pga_data_clean <- na.omit(pga_data)

ggplot(pga_data_clean, aes(x = Average_Drive, y = Average_Winnings)) +
  geom_point() +
  geom_smooth(method = "lm", col = "green") +
  labs(title = "Scatter Plot of Average Drive vs. Average Winnings", x = "Average Drive", y = "Average Winnings")
str(pga_data_clean)
remove_low_drives <- function(pga_data_clean) {
  filtered_data <- pga_data_clean %>%
    filter(Average_Drive >= 150)
  
  return(filtered_data)
}

# Example usage
pga_data_filtered <- remove_low_drives(pga_data_clean)
ggplot(pga_data_filtered, aes(x = Average_Drive, y = Average_Winnings)) +
  geom_point() +
  geom_smooth(method = "lm", col = "green") +
  labs(
    title = "Scatter Plot of Average Drive vs. Average Winnings (Filtered)",
    x = "Average Drive",
    y = "Average Winnings"
  ) +
  theme_minimal() 

pga_data_filtered$Age_Above_30 <- pga_data_filtered$Player_Age > 30

head(pga_data_filtered$Age_Above_30)
pga_data_filtered <- pga_data_filtered %>% select(-Player_name, -Driving_Accuracy, -Total_Winnings, -Average_number_putts, -Money_Rank, -Player_Age)
kable(head(pga_data_filtered))


# Standardizing Average_Winnings using z-scores
pga_data_filtered$Standardized_Winnings <- scale(pga_data_filtered$Average_Winnings)

# Updating the multiple regression model with standardized winnings
full.model <- lm(Standardized_Winnings ~ Average_Drive + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, 
                          data = pga_data_filtered)


colnames(pga_data_filtered)
kable(summary(full.model)$coef, caption ="Statistics of Regression Coefficients")

par(mfrow=c(2,2))
plot(full.model)

vif(full.model)
barplot(vif(full.model), main = "VIF Values", horiz = FALSE, col = "steelblue")

```


```{r echo=FALSE}
par(pty = "s", mfrow = c(2, 2), oma=c(.1,.1,.1,.1), mar=c(4, 0, 2, 0))
##
boxcox(Average_Winnings ~ log(Average_Drive) + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered, lambda = seq(-1, 1, length = 10), 
       xlab=expression(paste(lambda, ": log Average Drive")))
##
boxcox(Average_Winnings ~ Average_Drive + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered, lambda = seq(-1, 1, length = 10), 
       xlab=expression(paste(lambda, ": Average Drive")))
##
boxcox((Average_Winnings)^0.5 ~ Average_Drive + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered, lambda = seq(-1, 1, length = 10), 
       xlab=expression(paste(lambda, ": square root win")))
##
boxcox(Average_Winnings ~ log(Average_Drive) + Greens_on_reg +  Save_Percent + Number_events + log(1+Age_Above_30), data = pga_data_filtered, lambda = seq(-1, 1, length = 10), 
      xlab=expression(paste(lambda, ": log-age, log Average Drive")))

```

---

## Log Transformation Model


- Response variable – log (Average Winnings)
- Explanatory Variables – Average Drive, Greens on Regulation, Save Percentage, Number of Events, and Age Above 30

```{r echo=FALSE}
log.winnings = lm(log(Average_Winnings) ~ Average_Drive + Greens_on_reg +  Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered)
kable(summary(log.winnings)$coef, digits = 3)

```

---

## Goodness of Fit Measures

- Improvement in constant variance
- Improvement in Normality

```{r echo=FALSE}
par(mfrow = c(1,3))
plot(log.winnings)

```

---

## Comparison of Models

- Log model outperforms linear model 
- SSE signifies better fit
- R squared and R adjusted better in log model

```{r include=FALSE}
select=function(m){ 
 e = m$resid                           
 n0 = length(e)                        
 SSE=(m$df)*(summary(m)$sigma)^2       
 R.sq=summary(m)$r.squared             
 R.adj=summary(m)$adj.r               
 MSE=(summary(m)$sigma)^2              
 Cp=(SSE/MSE)-(n0-2*(n0-m$df))         
 AIC=n0*log(SSE)-n0*log(n0)+2*(n0-m$df)          
 SBC=n0*log(SSE)-n0*log(n0)+(log(n0))*(n0-m$df)  
 X=model.matrix(m)                     
 H=X%*%solve(t(X)%*%X)%*%t(X)          
 d=e/(1-diag(H))                       
 PRESS=t(d)%*%d   
 tbl = as.data.frame(cbind(SSE=SSE, R.sq=R.sq, R.adj = R.adj, Cp = Cp, AIC = AIC, SBC = SBC, PRD = PRESS))
 names(tbl)=c("SSE", "R.sq", "R.adj", "Cp", "AIC", "SBC", "PRESS")
 tbl
 }

```

```{r echo=FALSE}
output.sum = rbind(select(full.model), select(log.winnings))
row.names(output.sum) = c("full.model", "log.winnings")
kable(output.sum, digits=3)

```

---

## Comparison of Models Cont.

- Vast improvement in Log transformation model
- Normality?

```{r echo=FALSE}

par(pty = "s", mfrow = c(1, 2), mar = c(4, 4, 2, 1), oma = c(1, 1, 1, 1), cex.main = 1.2)

qqnorm(full.model$residuals, main = "Full Model Residuals")
qqline(full.model$residuals)

qqnorm(log.winnings$residuals, main = "Log Winnings Residuals")
qqline(log.winnings$residuals)


```

---

## Comparison of Model Cont.

- Residuals vs. Fitted improvement in log transformation
- Can assume constant variance

```{r echo=FALSE}
par(mfrow = c(1, 2))

plot(full.model$fitted.values, sqrt(abs(full.model$residuals)), 
     main = "Linear Model Scale-Location", xlab = "Fitted Values", ylab = "√|Residuals|")
lines(lowess(full.model$fitted.values, sqrt(abs(full.model$residuals))), col = "red", lwd = 2)

plot(log.winnings$fitted.values, sqrt(abs(log.winnings$residuals)), 
     main = "Log Model Scale-Location", xlab = "Fitted Values", ylab = "√|Residuals|")
lines(lowess(log.winnings$fitted.values, sqrt(abs(log.winnings$residuals))), col = "red", lwd = 2)

```
---
## 

<div style="display: flex; justify-content: center; align-items: center; height: 80vh; font-size: 50px;">
  Bootstrapping
</div>
---
## Bootstrapping

<div style="font-size: 26px; line-height: 2;">

<ul style="margin-top: 15px; margin-bottom: 15px;">

  <li>Have not assumed normality in our QQ plot.</li>  
  
  <li>Uses a nonparametric model for comparison.</li>  
  
  <li>Estimating confidence intervals.</li>  

</ul>

</div>

---
## Boostrapping Cont. with Cases

- The red line in the curves is used to show the p-values and uses the estimated regression coefficients and their corresponding standard error in the output of the regression procedure
- The blue curve is used to used to show the bootstrap CI which is based on a non-parametric data-driven estimate of the density of bootstrap sampling distribution
- All appear to be normal

```{r echo=FALSE}

log.winnings = lm(log(Average_Winnings) ~ Average_Drive + Greens_on_reg + Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered)

B = 1000  #

num.p = length(coef(log.winnings))  # number of parameters in the model (includes intercept)
smpl.n = nrow(pga_data_filtered)       # sample size

# Matrix to store bootstrap coefficients
coef.mtrx = matrix(0, nrow = B, ncol = num.p)

# Bootstrap loop
for (i in 1:B) {
  bootc.id = sample(1:smpl.n, smpl.n, replace = TRUE)  # Resample with replacement
  boot_data = pga_data_filtered[bootc.id, ]  # Create the bootstrap sample
  log.winnings.btc = lm(log(Average_Winnings) ~ Average_Drive + Greens_on_reg + Save_Percent + Number_events + Age_Above_30, data = boot_data)
  coef.mtrx[i, ] = coef(log.winnings.btc)  # Store the coefficients
}

boot.hist = function(cmtrx, bt.coef.mtrx, var.id, var.nm){

  x1.1 <- seq(min(bt.coef.mtrx[,var.id]), max(bt.coef.mtrx[,var.id]), length=300 )
  y1.1 <- dnorm(x1.1, mean(bt.coef.mtrx[,var.id]), sd(bt.coef.mtrx[,var.id]))

  highestbar = max(hist(bt.coef.mtrx[,var.id], plot = FALSE)$density) 
  ylimit <- max(c(y1.1,highestbar))
  hist(bt.coef.mtrx[,var.id], probability = TRUE, main = var.nm, xlab="", 
       col = "azure1",ylim=c(0,ylimit), border="lightseagreen")
  lines(x = x1.1, y = y1.1, col = "red3")
  lines(density(bt.coef.mtrx[,var.id], adjust=2), col="blue") 
  
}

par(mfrow=c(2,3), mar=c(5, 4, 4, 1), cex.main=1, cex.lab=0.9, cex.axis=0.8)

# Create your plots
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=1, var.nm ="Intercept" )
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=2, var.nm ="Average Drive" )
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=3, var.nm ="Greens On Regulation" )
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=4, var.nm ="Save Percentage" )
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=5, var.nm ="Number of Events" )
boot.hist(bt.coef.mtrx=coef.mtrx, var.id=6, var.nm ="Age Above 30" )



```
---
## Bootstrapping Cont. with Residuals

- The red line in the curves is used to show the p-values and uses the estimated regression coefficients and their corresponding standard error in the output of the regression procedure
- The blue curve is used to used to show the bootstrap CI which is based on a non-parametric data-driven estimate of the density of bootstrap sampling distribution
- Same output as cases

```{r include=FALSE}

num.p = dim(coef.mtrx)[2]  

btc.ci = NULL
btc.wd = NULL

for (i in 1:num.p) {
  lci.025 = round(quantile(coef.mtrx[, i], 0.025, type = 2), 8)
  uci.975 = round(quantile(coef.mtrx[, i], 0.975, type = 2), 8)
  btc.wd[i] = uci.975 - lci.025
  btc.ci[i] = paste("[", round(lci.025, 4), ", ", round(uci.975, 4), "]")
}

mean.coefs = apply(coef.mtrx, 2, mean)

results = as.data.frame(cbind(Mean_Coef = formatC(mean.coefs, 4, format = "f"), btc.ci.95 = btc.ci))

kable(results, caption = "Regression Coefficient Matrix with Bootstrap Confidence Intervals")

log.winnings <- lm(log(Average_Winnings) ~ Average_Drive + Greens_on_reg + Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered)
model.resid = log.winnings$residuals
B=1000
num.p = dim(model.matrix(log.winnings))[2]   
samp.n = dim(model.matrix(log.winnings))[1]  
btr.mtrx = matrix(rep(0,6*B), ncol=num.p)
for (i in 1:B){

  bt.lg.winnings = log.winnings$fitted.values + 
        sample(log.winnings$residuals, samp.n, replace = TRUE)  
  
  pga_data_filtered$bt.lg.winnings =  bt.lg.winnings   #  send the boot response to the data
  btr.model = lm(bt.lg.winnings ~ Average_Drive + Greens_on_reg + Save_Percent + Number_events + Age_Above_30, data = pga_data_filtered)  
  btr.mtrx[i,]=btr.model$coefficients
}
boot.hist = function(bt.coef.mtrx, var.id, var.nm){

  x1.1 <- seq(min(bt.coef.mtrx[,var.id]), max(bt.coef.mtrx[,var.id]), length=300 )
  y1.1 <- dnorm(x1.1, mean(bt.coef.mtrx[,var.id]), sd(bt.coef.mtrx[,var.id]))

  highestbar = max(hist(bt.coef.mtrx[,var.id], plot = FALSE)$density) 
  ylimit <- max(c(y1.1,highestbar))
  hist(bt.coef.mtrx[,var.id], probability = TRUE, main = var.nm, xlab="", 
       col = "azure1",ylim=c(0,ylimit), border="lightseagreen")
  lines(x = x1.1, y = y1.1, col = "red3")             
  lines(density(bt.coef.mtrx[,var.id], adjust=2), col="blue")    
} 



```

```{r echo=FALSE}
par(mfrow=c(2,3))  
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=1, var.nm ="Intercept" )
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=2, var.nm ="Average Drive" )
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=3, var.nm ="Greens on Regulation" )
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=4, var.nm ="Save Percentage" )
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=5, var.nm ="Number of Events" )
boot.hist(bt.coef.mtrx=btr.mtrx, var.id=6, var.nm ="Age" )


```
---
## Bootstrapping Cont. CIs

- CIs match our p-values
- Violation in two variables

```{r include=FALSE}
# Make sure the bootstrap results and summary are calculated before this chunk
num.p = dim(btr.mtrx)[2]  

# Calculate bootstrap confidence intervals for residuals
btr.ci = NULL
btr.wd = NULL

for (i in 1:num.p) {
  lci.025 = round(quantile(btr.mtrx[, i], 0.025, type = 2), 8)
  uci.975 = round(quantile(btr.mtrx[, i], 0.975, type = 2), 8)
  btr.wd[i] = uci.975 - lci.025
  btr.ci[i] = paste("[", round(lci.025, 4), ", ", round(uci.975, 4), "]")
}

# Create a summary table of coefficients with the bootstrap CIs
kable(as.data.frame(cbind(formatC(btr.mtrx[1, ], 4, format = "f"), btr.ci.95 = btr.ci)), 
      caption = "Regression Coefficient Matrix with 95% Residual Bootstrap CI")
```

```{r echo=FALSE}
# Summarize the coefficients with the CIs and p-values for final output
p_values <- summary(log.winnings)$coefficients[-3, 4]  

combined_matrix <- cbind(
  Coefficients = formatC(coef(log.winnings)[-3], 4, format = "f"),  
  `95% CI (Bootstrap t)` = btc.ci,                                
  `95% CI (Bootstrap r)` = btr.ci,                                 
  `p-values` = formatC(p_values, 4, format = "f")                  
)

library(knitr)
kable(as.data.frame(combined_matrix), 
      caption = "Final Combined Inferential Statistics: Coefficients, p-values, and Bootstrap CIs", digits = 3)
```
---
## Model Selection

<div style="font-size: 26px; line-height: 1.5;">

<ul style="margin-top: 15px; margin-bottom: 15px;">

  <li><u>Log Transformation</u>  
      <br> - Positives: Can assume normality and constant variance, best R-squared and adjusted R-squared values.  
      <br> - Negatives: Age and Average Drive are insignificant.</li>
  
  <li><u>Linear Model</u>  
      <br> - Positives: Only Age is insignificant, and the model is simple.  
      <br> - Negatives: Cannot assume constant variance or normality.</li>

</ul>

</div>

---
## 

<div style="display: flex; justify-content: center; align-items: center; height: 80vh; font-size: 50px;">
  Conclusion
</div>

---
## Conclusion

<div style="font-size: 26px; line-height: 2;">

<ul style="margin-top: 15px; margin-bottom: 15px;">
  
  <li>Greens on Regulation is the biggest indicator of increase in Winnings 21.18%.</li>
  
  <li>When holding all other variables constant, an increase of one unit in Average Drive leads to a 0.58% increase in Average Winnings.</li>
  
  <li>Short game (e.g., greens on regulation or save percent) has a larger impact on winnings compared to the long game. <br>
      - Short game impact:5.8% <br>
      - Long game (Average Drive) impact: 0.58%</li>
  
  <li>Number of Events decreases Average Winnings by 4.4%.</li>

</ul>

</div>


---
## Limitations

<div style="font-size: 26px; line-height: 2;">

<ul style="margin-top: 15px; margin-bottom: 15px;">

  <li>Average Drive and Age are insignificant values.</li>  
  
  <li>Log transformation is sensitive to outliers and could amplify small values.</li>  
  
  <li>Assumes a linear relationship.</li>  
  
  <li>Factors such as injury, weather, start time, and mental focus are not included in this dataset.</li>  

</ul>

</div>

---
## 

<div style="display: flex; justify-content: center; align-items: center; height: 80vh; font-size: 50px;">
  Questions?
</div>

---
## Works Cited

<div style="font-size: 35px; line-height: 1.5;">

<ul style="margin-top: 15px; margin-bottom: 15px;">

  <li>Datasets. (n.d.). <a href="https://users.stat.ufl.edu/~winner/datasets.html">https://users.stat.ufl.edu/~winner/datasets.html</a></li>  

</ul>

</div>

---
## 

<style>
  section {
    background-color: #A9D1D6;
    height: 100%;
  }
</style>

<div style="display: flex; justify-content: center; align-items: center; height: 100%; font-size: 50px;">
  Thank You!
</div>

---
## Slide Contributors

<style>
  section {
    background-color: #D1E2FF;
    height: 100%;
  }
</style>

<div style="font-size: 40px; line-height: 2;">
  <ul>
    <li>Ryan Lebo did slides from the Introduction to the Linear Regression Model</li>
    <li>Tyler Battaglini did the Box-Cox Transformation to the Conclusion</li>
  </ul>
</div>
