---
title: "Houston Weather Predictions"
subtitle: "&#127774;Time Series Model"  
author: "Tyler Battaglini"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)

# Detect, install and load packages if needed.
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
if (!require("MASS")) {
   install.packages("MASS")
   library(MASS)
}
if (!require("nleqslv")) {
   install.packages("nleqslv")
   library(nleqslv)
}
#
if (!require("pander")) {
   install.packages("pander")
   library(pander)
}

if (!require("psych")) {   
  install.packages("psych")
   library(psych)
}
if (!require("MASS")) {   
  install.packages("MASS")
   library(MASS)
}
if (!require("ggplot2")) {   
  install.packages("ggplot2")
   library(ggplot2)
}
if (!require("GGally")) {   
  install.packages("GGally")
   library(GGally)
}
if (!require("car")) {   
  install.packages("car")
   library(car)
}
if (!require("dplyr")) {   
  install.packages("dplyr")
   library(dplyr)
}
if (!require("caret")) {   
  install.packages("caret")
   library(caret)
}
if (!require("readxl")) {   
  install.packages("readxl")
   library(readxl)
}
if (!require("openxlsx")) {   
  install.packages("openxlsx")
   library(openxlsx)
}
if (!require("forecast")) {   
  install.packages("forecast")
   library(forecast)
}
# specifications of outputs of code in code chunks
knitr::opts_chunk$set(echo = TRUE,      # include code chunk in the output file
                      warnings = FALSE,  # sometimes, you code may produce warning messages,
                                         # you can choose to include the warning messages in
                                         # the output file. 
                      messages = FALSE,  #
                      results = TRUE,
                      
                      comment = NA       # you can also decide whether to include the output
                                         # in the output file.
                      )   
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

## Agenda

<ul style="font-size: 1.5em;">
  <li>Exploratory Data Analysis
    <ul>
      <li>Data Cleaning</li>
      <li>Accuracy Measure</li>
    </ul>
  </li>
  <li>Visualization
    <ul>
      <li>Model of Original Time Series</li>
      <li>Model of Forecasted Results</li>
    </ul>
  </li>
  <li>Final Model</li>
</ul>

---

## Exploratory Data Analysis

- Focus on the last 150 observations, split into 138 training and 12 test data points, with the training set converted to a monthly time series.
- Fit 8 different models to identify the best fit for the data.

```{r include=FALSE}

if (!requireNamespace("kableExtra", quietly = TRUE)) install.packages("kableExtra")
library(kableExtra)

weather <- read.csv("https://raw.githubusercontent.com/TylerBattaglini/STA-321/refs/heads/main/houston_weather.csv")

weather_subset <- tail(weather, 150)
train.weath = weather_subset$meanTemp[1:138]
test.weath = weather_subset$meanTemp[139:150]

weath = ts(train.weath, start=c(2000, 1), frequency=12)

fit1 = ses(weath, h=12)
fit2 = holt(weath, initial="optimal", h=12)
fit3 = holt(weath, damped=TRUE, h=12)
fit4 = holt(weath, exponential=TRUE, damped=TRUE, h=12)
fit5 = hw(weath, h=12, seasonal="additive")
fit6 = hw(weath, h=12, seasonal="multiplicative")
fit7 = hw(weath, h=12, seasonal="additive", damped=TRUE)
fit8 = hw(weath, h=12, seasonal="multiplicative", damped=TRUE)

```

```{r include=FALSE}
accuracy.table = round(rbind(accuracy(fit1), accuracy(fit2), accuracy(fit3), accuracy(fit4),
                             accuracy(fit5), accuracy(fit6), accuracy(fit7), accuracy(fit8)),4)
row.names(accuracy.table)=c("SES","Holt Linear","Holt Add. Damped", "Holt Exp. Damped",
                            "HW Add.","HW Exp.","HW Add. Damp", "HW Exp. Damp")
kable(accuracy.table, caption = "The accuracy measures of various exponential smoothing models 
      based on the training data")

```

```{r echo=FALSE}
# Load necessary libraries
library(kableExtra)

# Create and style the table
kable(accuracy.table, caption = "Accuracy Measures for Exponential Smoothing Models") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = TRUE, color = "white", background = "#1381B0") %>%
  row_spec(0, bold = TRUE, font_size = 14)

```


---
## Visualization

```{r echo=FALSE, fig.align='center', fig.width=9, fig.height=4.5, fig.cap="Comparing exponential smoothing models."}
par(mfrow=c(1,2), mar=c(3,3,2,1))  # Reduced top margin and figure height

pred.id = 139:150

# First Plot - Non-seasonal Models
plot(1:138, train.weath, lwd=2, type="o", ylab="Mean Temp", xlab="", 
     xlim=c(1,160), ylim=c(30, 90), cex=0.3, main="Non-seasonal Smoothing Models")
lines(pred.id, fit1$mean, col="red")
lines(pred.id, fit2$mean, col="blue")
lines(pred.id, fit3$mean, col="purple")
lines(pred.id, fit4$mean, col="navy")

points(pred.id, fit1$mean, pch=16, col="red", cex=0.5)
points(pred.id, fit2$mean, pch=17, col="blue", cex=0.5)
points(pred.id, fit3$mean, pch=19, col="purple", cex=0.5)
points(pred.id, fit4$mean, pch=21, col="navy", cex=0.5)

legend("bottomright", lty=1, col=c("red","blue","purple", "navy"), pch=c(16,17,19,21),
       legend=c("SES","Holt Linear","Holt Linear Damped", "Holt Multiplicative Damped"), 
       cex=0.7, bty="n")

# Second Plot - Seasonal Models
plot(1:138, train.weath, lwd=2, type="o", ylab="Mean Temp", xlab="", 
     xlim=c(1,160), ylim=c(30, 90), cex=0.3, main="HW Trend and Seasonal Smoothing Models")
lines(pred.id, fit5$mean, col="red")
lines(pred.id, fit6$mean, col="blue")
lines(pred.id, fit7$mean, col="purple")
lines(pred.id, fit8$mean, col="navy")

points(pred.id, fit5$mean, pch=16, col="red", cex=0.5)
points(pred.id, fit6$mean, pch=17, col="blue", cex=0.5)
points(pred.id, fit7$mean, pch=19, col="purple", cex=0.5)
points(pred.id, fit8$mean, pch=21, col="navy", cex=0.5)

legend("bottomright", lty=1, col=c("red","blue","purple", "navy"), pch=c(16,17,19,21),
       legend=c("HW Additive","HW Multiplicative","HW Additive Damped", "HW Multiplicative Damped"), 
       cex=0.7, bty="n")
```

---

## Final Model 

```{r include=FALSE}

acc.fun = function(test.data, mod.obj){
  PE=100*(test.data-mod.obj$mean)/mod.obj$mean
  MAPE = mean(abs(PE))
  ###
  E=test.data-mod.obj$mean
  MSE=mean(E^2)
  ###
  accuracy.metric=c(MSE=MSE, MAPE=MAPE)
  accuracy.metric
}



```

- HW.Add is the best model with lowest values
- Estimated values of the smoothing parameters in HW. Add
  - alpha -	0.1305680, beta	0.0001000, gamma	0.0001006

```{r echo=FALSE}

pred.accuracy = rbind(SES = acc.fun(test.data = test.weath, mod.obj = fit1),
                      Holt.Add = acc.fun(test.data = test.weath, mod.obj = fit2),
                      Holt.Add.Damp = acc.fun(test.data = test.weath, mod.obj = fit3),
                      Holt.Exp = acc.fun(test.data = test.weath, mod.obj = fit4),
                      HW.Add = acc.fun(test.data = test.weath, mod.obj = fit5),
                      HW.Exp = acc.fun(test.data = test.weath, mod.obj = fit6),
                      HW.Add.Damp = acc.fun(test.data = test.weath, mod.obj = fit7),
                      HW.Exp.Damp = acc.fun(test.data = test.weath, mod.obj = fit8))

kable(pred.accuracy, caption = "Final Accuracy Measures") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = "white", background = "#1381B0") %>%
  column_spec(2, color = "black", background = "#E2EAF0") %>%
  row_spec(0, bold = TRUE, font_size = 14, color = "white", background = "#2C3E50") %>%
  add_header_above(c("Model Accuracy" = 2, "MSE" = 1))
```

